---
title: "Plots Migration framing US and Canada"
output: html_document
---
```{r}
library(stm)
library(dplyr)
plot_dir = "~/Documents/BIGSSS/plots/"
opar = par()
```

 Make sure to load each trained model object and its corpus when you're generating the plots.
 
For example:

load("model_input_data/190507_can_out.RData.RData")
load("final_models/190131_interaction_model_spectral_content_can_justlibcon2.RData")

interaction_content_spec_can = interaction_content_spec
rm(interaction_content_spec)
out_can = out
rm(out)

load("model_input_data/190507_us_out.RData.RData")
load("final_models/190127_interaction_model_spectral_content_us.RData")

out_us = outm
interaction_content_spec_us = interaction_content_spec
rm(outm)
rm(interaction_content_spec)

Figure 5.7
```{r}
pdf(paste(c(plot_dir, "trafficking_plot_can", 15, ".pdf"), collapse = "_"))
plot(interaction_content_spec_can, type = "perspectives", covarlevels = c(1,2), topics = 15, plabels = c("conservative", "liberal"), text.cex = 1.2, n= 10, main = "Human Trafficking (15)", bty = 'n')
dev.off()
```


Canada Content plots
Figure 5.3b
```{r}
plot_labels_CAN = c('Immigration Types (5)', 'Asylum Process (10)', 'Law Enforcement (8)',
                    'Privacy or Security (14)','Security (17)', 'International Conflicts (18)',
                    'Budget (1)',  'Welfare (7)', 'Family Support (12)', 'Investment in Jobs (13)',
                    'Economic Sectors (16)', 'International Trade (20)', 'Citizenship (6)',
                    'Provincial Concerns (9)', 'History of Immigration (11)', 'Humanitarianism
                    (2)',
                    'Human Trafficking (15)')
for (i in c(5, 10, 8, 14, 17, 18, 1, 7, 12, 13, 16, 20, 6, 9, 11, 2, 15)){
  pdf(paste(c(plot_dir, "070519_CAN_content_plot", i, ".pdf"), collapse = "_"))
  plot(interaction_content_spec_can, type = "perspectives", covarlevels = c(1,2), topics = i, plabels = c("conservative", "liberal"), text.cex = 1.2, n= 10, main = plot_labels_CAN[i], bty = 'n')
  dev.off()
}
```


Figure 5.6
```{r}
pdf(paste(c(plot_dir, "trafficking_plot_us", 7, ".pdf"), collapse = "_"))
plot(interaction_content_spec_us, type = "perspectives", covarlevels = c(3,1), topics = 7, plabels = c(" Repub.", "Democ."), text.cex = 1.2, n= 10, main = "Human Trafficking (7)", bty = 'n')
dev.off()
```


5.6 a,b

```{r}
# trafficking topic comparison with content 
pdf(paste(c(plot_dir, "trafficking_plot_compare", 7, ".pdf"), collapse = "_"), colormodel = 'grey', pointsize = 10)
par(mfrow=c(2,1))
plot(interaction_content_spec_us, type = "perspectives", covarlevels = c(3,1), topics = 7, plabels = c(" Republican", "Democrat"), text.cex = 1.2, n= 10, main = "US Human Trafficking (7) (Fig. 5.6a)", bty = 'n')

plot(interaction_content_spec_can, type = "perspectives", covarlevels = c(1,2), topics = 15, plabels = c("conservative", "liberal"), text.cex = 1.2, n= 10, main = "Canada Human Trafficking (15) (Fig. 5.6b)", bty = 'n')
dev.off()
```


US Content plots - done 
Figure 5.3a
```{r}
plot_labels = c("Immigration Types (1)", "Law Enforcement (2)", "Security (10)",
                "International Conflicts (16)", "Threats (17)","Budget (12)",
                "Economy (13)", "Welfare (18)", "Voting (5)", "Multicultural America (6)",
                "Education (15)", "Human Trafficking (7)", "Foreign Aid (8)", "Humanitarianism
                (19)")
for (i in c(1,2,10,16,17, 12, 13, 18,5, 6, 15, 7, 8, 19)){
  pdf(paste(c(plot_dir, "070519_US_content_plot", i, ".pdf"), collapse = "_"), colormodel = 'grey')
  plot(interaction_content_spec_us, type = "perspectives", covarlevels = c(3,1), plabels = c("Republicans", "Democrats"), topics = i,   text.cex = 1.2, n= 10, main = plot_labels[i])
  dev.off()
}
```


```{r}
#Canada coeffplot
prep_all <- estimateEffect(c(1:20) ~ speakerparty * s(speechdate), interaction_content_spec_can, metadata = out_can$meta, uncertainty = "None")
#visualizes the differences between cons and lib parties for selected topics
pdf(paste(c(plot_dir, 'CAN_topics_migrcore_coeff.png'), collapse = ""), colormodel = 'grey')
Topicsm <-plot(prep_all, covariate = "speakerparty", topics = c(5, 10, 8, 14, 17, 18, 1, 7, 12, 13, 16, 20, 6, 9, 11, 2, 15), model = interaction_content_spec_can, method = "difference", cov.value1 = "liberal", cov.value2 = "conservative", ci.level = 0.95, xlab = "More conservative         More liberal", main = "Migration Topics in the Canadian Parliament",
               xlim = c(-.2, .2),labeltype = "custom",
               custom.labels = c('Immigration Types (5)', 'Asylum Process (10)',
                                 'Law Enforcement (8)', 'Privacy or Security (14)','Security
                                 (17)',
                                 'International Conflicts (18)', 'Budget (1)',  'Welfare (7)',
                                 'Family Support (12)', 'Investment \nin Jobs (13)', 'Economic
                                 Sectors (16)',
                                 'International Trade (20)', 'Citizenship (6)', 'Provincial
                                 Concerns (9)',
                                 'History of Immigration (11)', 'Humanitarianism (2)', 'Human
                                 Trafficking (15)'))
dev.off()
```

```{r}
# some renaming and data loading 
# load("final_models/190127_interaction_model_spectral_content_us.RData")
# interaction_content_spec_us = interaction_content_spec
# rm(interaction_content_spec)
# load("final_models/190131_interaction_model_spectral_content_can_justlibcon2.RData")
# interaction_content_spec_can = interaction_content_spec
# rm(interaction_content_spec)
# load("model_input_data/190507_us_out.RData.RData")
# out_us = outm
# rm(outm)
# load("model_input_data/190507_can_out.RData.RData")
# out_can = out 
# rm(out)
```
Figure 5.3 combined
```{r, fig.width=14, fig.height=12} 
pdf(paste(c(plot_dir, 'coeff_combined.pdf'), collapse = ""), colormodel = 'grey', pointsize = 10)
par(mfrow=c(1,2))
 #US coeffplot
prep_all <- estimateEffect(c(1:20) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
             
Topics <-plot(prep_all, covariate = "speakerparty", topics = c(1, 2, 10, 16, 17, 12, 13, 18, 5, 6, 15, 7, 8, 19),
model = interaction_content_spec_us, method = "difference", cov.value1 = "D", cov.value2 = "R", ci.level = 0.95, xlab = "More Republican         More Democrat", main = "Migration Topics in the US \n Congress (Figure 5.3a)", xlim = c(-.2, .2), labeltype = "custom",
custom.labels = c('Immigration Types (1)', 'Law Enforcement (2)',
                  'Security (10)', 'International Conflicts (16)',
                  'Threats (17)','Budget (12)', 'Oil Production (13)',
                  'Welfare (18)', 'Voting (5)', 'Multicultural America (6)',
                  'Education (15)', 'Human Trafficking (7)', 'Foreign Aid (8)',
                  'Humanitarianism (19)'), bty = 'n')
#Canada coeffplot
prep_all <- estimateEffect(c(1:20) ~ speakerparty * s(speechdate), interaction_content_spec_can, metadata = out_can$meta, uncertainty = "None")
#visualizes the differences between cons and lib parties for selected topics
Topicsm <-plot(prep_all, covariate = "speakerparty", topics = c(5, 10, 8, 14, 17, 18, 1, 7, 12, 13, 16, 20, 6, 9, 11, 2, 15), model = interaction_content_spec_can, method = "difference", cov.value1 = "liberal", cov.value2 = "conservative", ci.level = 0.95, xlab = "More conservative         More liberal", main = "Migration Topics in the Canadian \nParliament (Figure 5.3b)",
               xlim = c(-.2, .2),labeltype = "custom",
               custom.labels = c('Immigration Types (5)', 'Asylum Process (10)',
                                 'Law Enforcement (8)', 'Privacy or Security (14)','Security
                                 (17)',
                                 'International Conflicts (18)', 'Budget (1)',  'Welfare (7)',
                                 'Family Support (12)', 'Investment \nin Jobs (13)', 'Economic
                                 Sectors (16)',
                                 'International Trade (20)', 'Citizenship (6)', 'Provincial
                                 Concerns (9)',
                                 'History of Immigration (11)', 'Humanitarianism (2)', 'Human
                                 Trafficking (15)'), bty = 'n')
dev.off()
```


```{r}
```


Over time - cANADA plots
Figure 5.5
```{r}
 #gsub('-', '', as.character(out$meta$speechdate) ) %>% as.numeric()
#prep files for over time prevalence plots Canada
prep5 <- estimateEffect(c(5) ~ speakerparty * s(speechdate), interaction_content_spec_can,
metadata = out_can$meta, uncertainty = "None")
prep7 <- estimateEffect(c(7) ~ speakerparty * s(speechdate), interaction_content_spec_can,
metadata = out_can$meta, uncertainty = "None")
prep10 <- estimateEffect(c(10) ~ speakerparty * s(speechdate), interaction_content_spec_can,
metadata = out_can$meta, uncertainty = "None")
prep15<- estimateEffect(c(15) ~ speakerparty * s(speechdate), interaction_content_spec_can,
metadata = out_can$meta, uncertainty = "None")
prep17 <- estimateEffect(c(17) ~ speakerparty * s(speechdate), interaction_content_spec_can,
metadata = out_can$meta, uncertainty = "None")
```


```{r}
# canada over time
pdf(paste(c(plot_dir, 'CAN_4overtime.pdf'), collapse = ""),
    colormodel = 'grey', pointsize = 10)
par(mfrow=c(2,2))
plot(prep5, covariate = "speechdate", model =interaction_content_spec_can,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "conservative", linecol = "black", ylim = c(.0, .3),  main = "Immigration Types (5)",  printlegend = F, xaxt = 'n')
plot(prep5, covariate = "speechdate",  model =interaction_content_spec_can,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "liberal", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep5$data$speechdate, n = 4), labels=pretty(prep5$data$speechdate)/ 10000)
legend(19950000, 0.3, cex = 0.90, c("liberals", "conservatives"), lwd = 2, col=c("snow4","black"))
plot(prep10, covariate = "speechdate",  model =interaction_content_spec_can,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "conservative", linecol = "black", ylim = c(.0, .3),  main = "Asylum Process (10)",  printlegend = F, xaxt = 'n')
plot(prep10, covariate = "speechdate",  model =interaction_content_spec_can,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "liberal", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep10$data$speechdate, n = 4), labels=pretty(prep10$data$speechdate)/ 10000)
legend(19950000, .3, cex = 0.90, c("liberals", "conservatives"), lwd = 2, col = c("snow4", "black"))
plot(prep15, covariate = "speechdate",  model =interaction_content_spec_can,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "conservative", linecol = "black", ylim = c(.0, .3), main = "Human Trafficking (15)",  printlegend = F, xaxt = 'n')
plot(prep15, covariate = "speechdate", model =interaction_content_spec_can,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "liberal", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep15$data$speechdate, n = 4), labels=pretty(prep15$data$speechdate)/ 10000)
legend(19950000, .3, cex = 0.90, c("liberals", "conservatives"), lwd = 2, col = c("snow4", "black"))
plot(prep17, covariate = "speechdate", model =interaction_content_spec_can,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "conservative", linecol = "black", ylim = c(.0, .3),  main = "Security (17)",  printlegend = F, xaxt = 'n')
plot(prep17, covariate = "speechdate",  model =interaction_content_spec_can,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "liberal", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep17$data$speechdate, n = 4), labels=pretty(prep17$data$speechdate)/ 10000)
legend(20030000, .3,cex = 0.90, c("liberals", "conservatives"), lwd = 2, col = c("snow4", "black"))
dev.off()
```


Over time - US plots
Figure 5.4
```{r}
#interactionm = interaction_content_spec
#prep files for over time prevalence plots United States
prep1 <- estimateEffect(c(1) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep2 <- estimateEffect(c(2) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep5 <- estimateEffect(c(5) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep6 <- estimateEffect(c(6) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep7 <- estimateEffect(c(7) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep8 <- estimateEffect(c(8) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep10 <- estimateEffect(c(10) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep16 <- estimateEffect(c(16) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep17 <- estimateEffect(c(17) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep19 <- estimateEffect(c(19) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
prep20 <- estimateEffect(c(20) ~ speakerparty * s(speechdate),interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
```

```{r}
# uS over time prevalence plots
pdf(paste(c(plot_dir, 'US_4overtime.pdf'), collapse = ""),
     colormodel = 'grey', pointsize = 10)
par(mfrow=c(2,2))
plot(prep1, covariate = "speechdate", model =interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "R", linecol = "black", ylim = c(.0, .3),  main = "Immigration Types (1)",  printlegend = F, xaxt = 'n')
plot(prep1, covariate = "speechdate", model = interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "D", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep1$data$speechdate, n = 4), labels=pretty(prep1$data$speechdate)/ 10000)
legend(19950000, .3, c("Democrats", "Republicans"), lwd = 2, col = c("snow4", "black"))
plot(prep2, covariate = "speechdate", model =interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "R", linecol = "black", ylim = c(.0, .3),  main = "Law Enforcement (2)",  printlegend = F, xaxt = 'n')
plot(prep2, covariate = "speechdate", model = interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "D", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep2$data$speechdate, n = 4), labels=pretty(prep2$data$speechdate)/ 10000)
legend(19950000, .3, c("Democrats", "Republicans"), lwd = 2, col = c("snow4", "black"))
plot(prep7, covariate = "speechdate", model =interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "R", linecol = "black", ylim = c(.0, .3),  main = "Human Trafficking (7)",  printlegend = F, xaxt = 'n')
plot(prep7, covariate = "speechdate", model = interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "D", linecol = "snow4", add = T, printlegend = F, xaxt = 'n')
axis(side=1, at = pretty(prep7$data$speechdate, n = 4), labels=pretty(prep7$data$speechdate)/ 10000)
legend(19950000, .3, c("Democrats", "Republicans"), lwd = 2, col = c("snow4", "black"))
plot(prep10, covariate = "speechdate", model =interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "R", linecol = "black", ylim = c(.0, .3),  main = "Security (10)",  printlegend = F, xaxt = 'n')
axis(side=1, at = pretty(prep10$data$speechdate, n = 4), labels=pretty(prep10$data$speechdate)/ 10000)
plot(prep10, covariate = "speechdate", model = interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "D",  linecol = "snow4", add = T, printlegend = F, xaxt = 'n')
legend(19950000, .3, c("Democrats", "Republicans"), lwd = 2, col = c("snow4", "black"))
dev.off()
```


Figure 5.2a,b
```{r}
pdf(paste(c(plot_dir, 'expected_proportion_combined.pdf'), collapse = ""),
     colormodel = 'grey', pointsize = 10, width = 10)
par(mfrow=c(1,2))
plot(interaction_content_spec_us,  custom.labels = c("Immigration Types", "Law Enforcement", "Procedural 1", "Wildlife Refuge", "Voting",
                "Multicultural America", "Human trafficking", "Foreign Aid",
                "Procedural 2", "Security", "Procedural 3","Budget 12", "Oil Production", 
                "Procedural 4",
                "Education", "International conflicts", "Threats",
                "Welfare", "Humanitarianism", "Procedural 5"), type = "summary", main = "Top Topics - US Corpus \n(Figure 5.2a)", xlim = c(0, .3), bty = 'n')
plot(interaction_content_spec_can,  custom.labels = c('Budget', 'Humanitarianism', 'First Nations', 'Procedural 1', 'Immigration Types',
                    'Citizenship','Welfare', 'Law Enforcement', 'Provincial Concerns','Asylum Process',
                    'History of Immigration', 'Family Support', 'Investment in Jobs', 'Privacy or Security',
                    'Human Trafficking','Economic Sectors','Security',
                    'International Conflicts', 'Procedural 2','International Trade'), type = "summary", main = "Top Topics - Canada Corpus \n(Figure 5.2b)", xlim = c(0, .3), bty = 'n')
dev.off()
```

Figure 5.1
```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
topicClassUSA <-rbind("Migration Core","Migration Core", "Irrelevant", "Irrelevant", "Culture", "Irrelevant",
                "Human Rights", "Human Rights", "Irrelevant", "Security", "Irrelevant", "Economy", "Economy",
                "Irrelevant", "Culture", "Security", "Security", "Economy", "Human Rights", "Irrelevant")
USA <- rbind("United States", "United States", "United States", "United States", "United States", "United States", 
             "United States", "United States", "United States", "United States", "United States", "United States", 
             "United States", "United States", "United States", "United States", "United States", "United States", 
             "United States", "United States")
topicClassUSA <- as.data.frame(cbind(topicClassUSA, USA))
colnames(topicClassUSA)[1] <- "Category"
colnames(topicClassUSA)[2] <- "Country"
topicClassCAN <- rbind("Economy", "Migration Core", "Irrelevant", "Irrelevant", "Migration Core",
                       "Culture", "Economy", "Security", "Culture", "Migration Core", "Culture", "Economy", 
                       "Economy", "Security","Human Rights", "Economy", "Security", "Security", "Irrelevant", "Economy")
CAN <- rbind("Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", 
             "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada", "Canada")
topicClassCAN <- as.data.frame(cbind(topicClassCAN, CAN))
colnames(topicClassCAN)[1] <- "Category"
colnames(topicClassCAN)[2] <- "Country"
dat <- rbind(topicClassUSA, topicClassCAN)
#write.csv(dat, "data.BIGSSS.csv")
#here, i took it into excel to add the counts, I know there's a tidyr way to do it but alas, here we are.
#dat<- read.csv("data.fortopiccategorization.BIGSSS.csv")
# ref https://stackoverflow.com/questions/2479689/crosstab-with-multiple-items
dat_sum = data.frame(xtabs(~Country+Category, data = dat))
#dat_sum$Country = factor(dat_sum$Country, levels = rev(levels(dat_sum$Country)))
dat_sum$Category = factor(dat_sum$Category, levels = rev(c("Security", "Migration Core", "Human Rights", "Economy", "Culture", "Irrelevant")))
pdf(paste(c(plot_dir, 'topic_classifications.pdf'), collapse = ""),
    colormodel = 'grey')

Both_Plot = ggplot(data=dat_sum, aes(Category, Freq)) +
  geom_bar(aes(fill=Country), position = position_dodge(width = 1), stat="identity") +
  scale_fill_grey(start = 0.25, end = 0.75) +
  xlab("Topic Category") + 
  coord_flip() +
  ylab("Count" ) +
  ggtitle("Topic Classification")
theme_set(theme_bw())
theme_update(text = element_text(size=16),
             panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             strip.background = element_blank()
)
# reverse legend order
Both_Plot +  guides(fill =  guide_legend(reverse = TRUE))
dev.off()
#Both_Plot
```