---
title: "Plots Migration framing US and Canada"
output: html_document
---
```{r}
library(stm)
library(dplyr)
plot_dir = "~/Documents/BIGSSS/plots/"
opar = par()
```

 Make sure to load each trained model object and its corpus when you're generating the plots.
 
For example:

load("model_input_data/190507_can_out.RData.RData")
load("final_models/190131_interaction_model_spectral_content_can_justlibcon2.RData")
load("model_input_data/190507_us_out.RData.RData")
load("final_models/190127_interaction_model_spectral_content_us.RData")

Canada Content plots
```{r}

plot_labels_CAN = c('Immigration Types (5)', 'Asylum Process (10)', 'Law Enforcement (8)',
                    'Privacy or Security (14)','Security (17)', 'International Conflicts (18)',
                    'Budget (1)',  'Welfare (7)', 'Family Support (12)', 'Investment in Jobs (13)',
                    'Economic Sectors (16)', 'International Trade (20)', 'Citizenship (6)',
                    'Provincial Concerns (9)', 'History of Immigration (11)', 'Humanitarianism
                    (2)',
                    'Human Trafficking (15)')


for (i in c(5, 10, 8, 14, 17, 18, 1, 7, 12, 13, 16, 20, 6, 9, 11, 2, 15)){
  png(paste(c(plot_dir, "070519_CAN_content_plot", i, ".png"), collapse = "_"))
  plot(interaction_content_spec, type = "perspectives", covarlevels = c(1,2), topics = i, plabels = c(" cons.", "lib."), text.cex = 0.9, n= 10, main = plot_labels_CAN[i])
  dev.off()
}
```

US Content plots - done 

```{r}
plot_labels = c("Immigration Types (1)", "Law Enforcement (2)", "Security (10)",
                "International Conflicts (16)", "Threats (17)","Budget (12)",
                "Economy (13)", "Welfare (18)", "Voting (5)", "Multicultural America (6)",
                "Education (15)", "Human Trafficking (7)", "Foreign Aid (8)", "Humanitarianism
                (19)")




for (i in c(1,2,10,16,17, 12, 13, 18,5, 6, 15, 7, 8, 19)){
  png(paste(c(plot_dir, "070519_US_content_plot", i, ".png"), collapse = "_"))
  plot(interaction_content_spec, type = "perspectives", covarlevels = c(3,1), plabels = c("Republicans", "Democrats"), topics = i,   text.cex = 1, n= 10, main = plot_labels[i])
  dev.off()
}
```


```{r}
#Canada coeffplot
prep_all <- estimateEffect(c(1:20) ~ speakerparty * s(speechdate), interaction_content_spec, metadata = out$meta, uncertainty = "None")

#visualizes the differences between cons and lib parties for selected topics


png(paste(c(plot_dir, 'CAN_topics_migrcore_coeff.png'), collapse = ""))

Topicsm <-plot(prep_all, covariate = "speakerparty", topics = c(5, 10, 8, 14, 17, 18, 1, 7, 12, 13, 16, 20, 6, 9, 11, 2, 15), model = interaction_content_spec, method = "difference", cov.value1 = "liberal", cov.value2 = "conservative", ci.level = 0.95, xlab = "More conservative         More liberal", main = "Migration Topics in the Canadian Parliament",
               xlim = c(-.2, .2),labeltype = "custom",
               custom.labels = c('Immigration Types (5)', 'Asylum Process (10)',
                                 'Law Enforcement (8)', 'Privacy or Security (14)','Security
                                 (17)',
                                 'International Conflicts (18)', 'Budget (1)',  'Welfare (7)',
                                 'Family Support (12)', 'Investment \nin Jobs (13)', 'Economic
                                 Sectors (16)',
                                 'International Trade (20)', 'Citizenship (6)', 'Provincial
                                 Concerns (9)',
                                 'History of Immigration (11)', 'Humanitarianism (2)', 'Human
                                 Trafficking (15)'))

dev.off()
```
```{r}
# some renaming and data loading 
load("final_models/190127_interaction_model_spectral_content_us.RData")
interaction_content_spec_us = interaction_content_spec
rm(interaction_content_spec)
load("final_models/190131_interaction_model_spectral_content_can_justlibcon2.RData")
interaction_content_spec_can = interaction_content_spec
rm(interaction_content_spec)

load("model_input_data/190507_us_out.RData.RData")
out_us = outm
rm(outm)

load("model_input_data/190507_can_out.RData.RData")
out_can = out 
rm(out)
```

```{r, fig.width=14, fig.height=12} 

png(paste(c(plot_dir, 'coeff_combined.png'), collapse = ""), res = 50)
par(mfrow=c(1,2))
 #US coeffplot

prep_all <- estimateEffect(c(1:20) ~ speakerparty * s(speechdate), interaction_content_spec_us,
metadata = out_us$meta, uncertainty = "None")
             
Topics <-plot(prep_all, covariate = "speakerparty", topics = c(1, 2, 10, 16, 17, 12, 13, 18, 5, 6, 15, 7, 8, 19),
model = interaction_content_spec_us, method = "difference", cov.value1 = "D", cov.value2 = "R", ci.level = 0.95, xlab = "More Republican         More Democrat", main = "Migration Topics in the US Congress", xlim = c(-.2, .2), labeltype = "custom",
custom.labels = c('Immigration Types (1)', 'Law Enforcement (2)',
                  'Security (10)', 'International Conflicts (16)',
                  'Threats (17)','Budget (12)', 'Oil Production (13)',
                  'Welfare (18)', 'Voting (5)', 'Multicultural America (6)',
                  'Education (15)', 'Human Trafficking (7)', 'Foreign Aid (8)',
                  'Humanitarianism (19)'), bty = 'n')


#Canada coeffplot
prep_all <- estimateEffect(c(1:20) ~ speakerparty * s(speechdate), interaction_content_spec_can, metadata = out_can$meta, uncertainty = "None")

#visualizes the differences between cons and lib parties for selected topics

Topicsm <-plot(prep_all, covariate = "speakerparty", topics = c(5, 10, 8, 14, 17, 18, 1, 7, 12, 13, 16, 20, 6, 9, 11, 2, 15), model = interaction_content_spec_can, method = "difference", cov.value1 = "liberal", cov.value2 = "conservative", ci.level = 0.95, xlab = "More conservative         More liberal", main = "Migration Topics in the Canadian Parliament",
               xlim = c(-.2, .2),labeltype = "custom",
               custom.labels = c('Immigration Types (5)', 'Asylum Process (10)',
                                 'Law Enforcement (8)', 'Privacy or Security (14)','Security
                                 (17)',
                                 'International Conflicts (18)', 'Budget (1)',  'Welfare (7)',
                                 'Family Support (12)', 'Investment \nin Jobs (13)', 'Economic
                                 Sectors (16)',
                                 'International Trade (20)', 'Citizenship (6)', 'Provincial
                                 Concerns (9)',
                                 'History of Immigration (11)', 'Humanitarianism (2)', 'Human
                                 Trafficking (15)'), bty = 'n')
dev.off()
```


```{r}
# combined us and canada coefficient plot 
png(paste(c(plot_dir, 'coeff_combined.png'), collapse = ""))
par(mfrow=c(2,1))

 #US coeffplot
prep_all <- estimateEffect(c(1:20) ~ speakerparty * s(speechdate), interaction_content_spec,
metadata = out_us$meta, uncertainty = "None")
             
Topics <-plot(prep_all, covariate = "speakerparty", topics = c(1, 2, 10, 16, 17, 12, 13, 18, 5, 6, 15, 7, 8, 19),
model = interaction_content_spec, method = "difference", cov.value1 = "D", cov.value2 = "R", ci.level = 0.95, xlab = "More Republican         More Democrat", main = "Migration Topics in the US Congress", xlim = c(-.2, .2), labeltype = "custom",
custom.labels = c('Immigration Types (1)', 'Law Enforcement (2)',
                  'Security (10)', 'International Conflicts (16)',
                  'Threats (17)','Budget (12)', 'Oil Production (13)',
                  'Welfare (18)', 'Voting (5)', 'Multicultural America (6)',
                  'Education (15)', 'Human Trafficking (7)', 'Foreign Aid (8)',
                  'Humanitarianism (19)'))


dev.off()
```


Over time - cANADA plots

```{r}
 #gsub('-', '', as.character(out$meta$speechdate) ) %>% as.numeric()


#prep files for over time prevalence plots Canada



prep5 <- estimateEffect(c(5) ~ speakerparty * s(speechdate), interaction_content_spec,
metadata = out$meta, uncertainty = "None")

prep7 <- estimateEffect(c(7) ~ speakerparty * s(speechdate), interaction_content_spec,
metadata = out$meta, uncertainty = "None")

prep10 <- estimateEffect(c(10) ~ speakerparty * s(speechdate), interaction_content_spec,
metadata = out$meta, uncertainty = "None")


prep15<- estimateEffect(c(15) ~ speakerparty * s(speechdate), interaction_content_spec,
metadata = out$meta, uncertainty = "None")


prep17 <- estimateEffect(c(17) ~ speakerparty * s(speechdate), interaction_content_spec,
metadata = out$meta, uncertainty = "None")

```


```{r}
# canada over time
png(paste(c(plot_dir, 'CAN_4overtime.png'), collapse = ""))
par(mfrow=c(2,2))


plot(prep5, covariate = "speechdate", model =interaction,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "conservative", linecol = "black", ylim = c(-.1, .3),  main = "Immigration Types (5)",  printlegend = F, xaxt = 'n')
plot(prep5, covariate = "speechdate", model = interaction,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "liberal", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep5$data$speechdate, n = 4), labels=pretty(prep5$data$speechdate)/ 10000)
legend(19950000, 0, cex = 0.90, c("liberals", "conservatives"), lwd = 2, col=c("snow4","black"))


plot(prep10, covariate = "speechdate", model =interaction,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "conservative", linecol = "black", ylim = c(-.1, .3),  main = "Asylum Process (10)",  printlegend = F, xaxt = 'n')
plot(prep10, covariate = "speechdate", model = interaction,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "liberal", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep10$data$speechdate, n = 4), labels=pretty(prep10$data$speechdate)/ 10000)
legend(19950000, .0, cex = 0.90, c("liberals", "conservatives"), lwd = 2, col = c("snow4", "black"))

plot(prep15, covariate = "speechdate", model =interaction,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "conservative", linecol = "black", ylim = c(-.1, .3), main = "Human Trafficking (15)",  printlegend = F, xaxt = 'n')
plot(prep15, covariate = "speechdate", model = interaction,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "liberal", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep15$data$speechdate, n = 4), labels=pretty(prep15$data$speechdate)/ 10000)
legend(19950000, .3, cex = 0.90, c("liberals", "conservatives"), lwd = 2, col = c("snow4", "black"))


plot(prep17, covariate = "speechdate", model =interaction,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "conservative", linecol = "black", ylim = c(-.1, .3),  main = "Security (17)",  printlegend = F, xaxt = 'n')
plot(prep17, covariate = "speechdate", model = interaction,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "liberal", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep17$data$speechdate, n = 4), labels=pretty(prep17$data$speechdate)/ 10000)
legend(20030000, .3,cex = 0.90, c("liberals", "conservatives"), lwd = 2, col = c("snow4", "black"))


dev.off()
```


Over time - US plots

```{r}
interactionm = interaction_content_spec
#prep files for over time prevalence plots United States
prep1 <- estimateEffect(c(1) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep2 <- estimateEffect(c(2) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep5 <- estimateEffect(c(5) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep6 <- estimateEffect(c(6) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep7 <- estimateEffect(c(7) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep8 <- estimateEffect(c(8) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep10 <- estimateEffect(c(10) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep16 <- estimateEffect(c(16) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep17 <- estimateEffect(c(17) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep19 <- estimateEffect(c(19) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")

prep20 <- estimateEffect(c(20) ~ speakerparty * s(speechdate), interactionm,
metadata = outm$meta, uncertainty = "None")
```

```{r}
# uS over time prevalence plots


png(paste(c(plot_dir, 'US_4overtime.png'), collapse = ""))
par(mfrow=c(2,2))

plot(prep1, covariate = "speechdate", model =interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "R", linecol = "black", ylim = c(.0, .3),  main = "Immigration Types (1)",  printlegend = F, xaxt = 'n')
plot(prep1, covariate = "speechdate", model = interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "D", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep1$data$speechdate, n = 4), labels=pretty(prep1$data$speechdate)/ 10000)
legend(19950000, .3, c("Democrats", "Republicans"), lwd = 2, col = c("snow4", "black"))


plot(prep2, covariate = "speechdate", model =interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "R", linecol = "black", ylim = c(.0, .3),  main = "Law Enforcement (2)",  printlegend = F, xaxt = 'n')
plot(prep2, covariate = "speechdate", model = interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "D", linecol = "snow4", add = T, printlegend = F,xaxt = 'n')
axis(side=1, at = pretty(prep2$data$speechdate, n = 4), labels=pretty(prep2$data$speechdate)/ 10000)
legend(19950000, .3, c("Democrats", "Republicans"), lwd = 2, col = c("snow4", "black"))


plot(prep7, covariate = "speechdate", model =interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "R", linecol = "black", ylim = c(.0, .3),  main = "Human Trafficking (7)",  printlegend = F, xaxt = 'n')
plot(prep7, covariate = "speechdate", model = interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "D", linecol = "snow4", add = T, printlegend = F, xaxt = 'n')
axis(side=1, at = pretty(prep7$data$speechdate, n = 4), labels=pretty(prep7$data$speechdate)/ 10000)
legend(19950000, .3, c("Democrats", "Republicans"), lwd = 2, col = c("snow4", "black"))

plot(prep10, covariate = "speechdate", model =interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty", ci.level = 0.95, moderator.value = "R", linecol = "black", ylim = c(.0, .3),  main = "Security (10)",  printlegend = F, xaxt = 'n')
axis(side=1, at = pretty(prep10$data$speechdate, n = 4), labels=pretty(prep10$data$speechdate)/ 10000)

plot(prep10, covariate = "speechdate", model = interaction_content_spec,
method = "continuous", xlab = "Date", moderator = "speakerparty",
moderator.value = "D",  linecol = "snow4", add = T, printlegend = F, xaxt = 'n')
legend(19950000, .3, c("Democrats", "Republicans"), lwd = 2, col = c("snow4", "black"))

dev.off()
```
